### 2019-06-05 05_approximation.tex
update

\begin{figure*}
%\vspace{-0.15in}
% \begin{figure}[H]
	\begin{center}
% 		\includegraphics[width=2.5in]{figures/mapp}
		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
	\end{center}
%\vspace{-0.2in}
	\caption{(left) A dual-arm rearrangement problem. (middle) The same problem as minimum weight edge matching on a fully connected directed graph of \textit{transfers}. (right) The ordering of the object-arm assignments from an optimal tour over a \textit{transit} graph.}
%	\vspace{-0.2in}
	\label{fig:edge_matching}
% \end{figure}
%\vspace{-0.1in}
\end{figure*}

>>>>

\begin{figure*}
%\vspace{-0.15in}
% \begin{figure}[H]
	\begin{center}
% 		\includegraphics[width=2.5in]{figures/mapp}
%		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
		\includegraphics[width=0.8\textwidth]{figures/algo_1}
		\includegraphics[width=0.8\textwidth]{figures/algo_2}
	\end{center}
%\vspace{-0.2in}
	\caption{\textit{(Top-left)} A dual-arm rearrangement problem. \textit{(Top)} The problem of optimizing object transfers reduces to a minimum weight edge matching on a fully connected directed graph of \textit{transfers}. \textit{(Bottom)} Each transit moves the arms from the target poses of the current objects, to the initial poses of the next objects in the object-arm assignments. The ordering of the object-arm assignments form an optimal tour over a \textit{transit} graph.}
%	\vspace{-0.2in}
	\label{fig:edge_matching}
% \end{figure}
%\vspace{-0.1in}
\end{figure*}
